---
title: "Web Scrapping for Palestine"
author: "Shea Turner-Matthews"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction

News outlets across the USA as well as many other countries of the world are portraying the situation in Palestine from a biased lense that tends to invalidate Palestinian perspectives and glorify those of Israel and the Israeli military. In this project I will attempt to showcase these biases be analyzing the language used in news articles.

## 2. Data

I will be web scraping data off of Google news, Google search, and other news platforms. I will be scraping the article titles, names of the journal, and dates of release. 

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readxl)
```

```{r read_in_data}
Palestine_news_articles <- read_xlsx("../data/Palestine_news_articles.xlsx")
Israel_news_articles <- read_xlsx("../data/israel_news_articles.xlsx")
Gaza_news_articles <- read_xlsx("../data/gaza_news_articles.xlsx")
```


```{r palestine}
tidy_pna <- Palestine_news_articles %>% 
  select("...2", "...3", "...4", "...5") %>% 
  rename("title" = "...2",
         "journal" = "...3",
         "date" = "...4",
         "description" = "...5") %>% 
  filter(!is.na(title)) %>% 
  filter(title != "Title",
         journal != "Journal",
         date != "Date",
         description != "Description") %>% 
  filter(!str_starts(journal, "#")) %>% 
  mutate(keyword = "palestine")
```

```{r israel}
tidy_ina <- Israel_news_articles %>% 
  select("...2", "...3", "...4", "...5") %>% 
  rename("title" = "...2",
         "journal" = "...3",
         "date" = "...4",
         "description" = "...5") %>% 
  filter(!is.na(title)) %>% 
  filter(title != "Title",
         journal != "Journal",
         date != "Date",
         description != "Description") %>% 
  filter(!str_starts(journal, "#")) %>% 
  mutate(keyword = "israel")
```

```{r gaza}
tidy_gna <- Gaza_news_articles %>% 
  select("...2", "...3", "...4", "...5") %>% 
  rename("title" = "...2",
         "journal" = "...3",
         "date" = "...4",
         "description" = "...5") %>% 
  filter(!is.na(title)) %>% 
  filter(title != "Title",
         journal != "Journal",
         date != "Date",
         description != "Description") %>% 
  filter(!str_starts(journal, "#")) %>% 
  mutate(keyword = "gaza")
```

```{r joining}
joining <- full_join(tidy_pna, tidy_gna)
all_data <- full_join(joining, tidy_ina)
```

```{r}
glimpse(all_data)
```


```{r most_common_articles_in_each_dataset}
tidy_pna %>%
  count(journal) %>%
  top_n(10, n) %>%
  ggplot(aes(x = reorder(journal, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(x = "Journal", y = "Frequency") +
  theme_minimal()

tidy_ina %>%
  count(journal) %>%
  top_n(10, n) %>%
  ggplot(aes(x = reorder(journal, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(x = "Journal", y = "Frequency") +
  theme_minimal()

tidy_gna %>%
  count(journal) %>%
  top_n(10, n) %>%
  ggplot(aes(x = reorder(journal, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(x = "Journal", y = "Frequency") +
  theme_minimal()
```

## 3. Ethics review

I am not 100% percent sure whether or not scrapping data off of Google search is fully legal. However, all of this information is publically accessible, and I do not intend to do anything formal with the data. Rather, this work will only be for the final project for this class and my own curiosity. Therefore, I do not see anything ethically wrong with doing this project.

## 4. Data analysis plan

I will compare the most common words used across articles and frequencies of words used by different journals and news outlets. I also wish to look at relationships between words. (ex. which words are most commonly proceed the word "Palestine"). In addition to comparing words used by different journals, I would also like to look at how the overall use of language changes over time. I will do this by looking at a specific set of words and plotting there average use over time. 

